Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-09-12 paper/virtual_cytoplasm_v2.tex
Makefile
radial distribution function for metabolites and rna with reference to mg is added
adjustment to figure lables, rmsf plot is updated

%\begin{affiliations}
%\item 
%  \item Department of Biological Science and Engineering, School of Chemistry and Biological Engineering, University of Science and Technology Beijing, 100083 Beijing, China
%\end{affiliations}

@@

% General Simulation setup:
% \begin{itemize}
% \item Force Field
% \item Water model
% \item Gromacs
% \item Temperature and pressure
% \item (details of soup box)
% \item Minimization 
% \item Equilibration
% \item Production
% \end{itemize}

% \begin{itemize}
% \item Box building
% \item Droplets
% \item Shrinking
% \end{itemize}

@@

% We followed the Lipari-Szabo approach to calculate the rotational correlation time, using a second order Legendre polynomial $P_2({\mathbf r}_{NH})$ to be able to compare the results to experimental relaxation data~\cite{Lipari1982b}. First the average order parameter $<\!\!S^2\!\!>$ over all ${\mathbf r}_{NH}$ vectors for each protein was determined from trajectories after the biomolecular rotation- and translation-movements were removed. Then the rotational correlation function $C(t)$ of the original trajectories was fitted to 
% \begin{equation}
% C(t) ~=~ <\!\!S^2\!\!> \exp(-t/\tau_M) + (1-<\!\!S^2\!\!>)\exp(-t/\tau_T)
% \end{equation}
% where $\tau_M$ is the rotational correlation time (tumbling) and $\tau_T = (\tau_M^{-1} + \tau_e^{-1})^{-1}$, where $\tau_e$ is the internal bond movement.

@@

\begin{figure}
\includegraphics[scale=0.6]{avclust.pdf}
\caption{Number of metabolite molecules that form a cluster in cytoplasm simulations.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{nclust.pdf}
\caption{Number of clusters that form during the cytoplasm simulations.}
\end{figure}

@@

\bibliography{library}

% \begin{addendum}
%  \item  
%  \item[Competing Interests] 
%  \item[Correspondence]  
% \end{addendum}

@@

% Cytoplasm setup:
% \begin{itemize}
% \item Constitutents of the cytoplasm in ratio, (non-ribomosal) protein, (non-ribosomal) RNA and metabolites {\bf review paper}
% \item Proteins fraction 
% \item Nucleic Acid fraction
% \item Metabolites fraction
% \item Physiological condition of the cell
% \item Biomolecular fraction 
% \end{itemize}

% General Simulation setup:
% \begin{itemize}
% \item Force Field
% \item Water model
% \item Gromacs
% \item Temperature and pressure
% \item (details of soup box)
% \item Minimization 
% \item Equilibration
% \item Production
% \end{itemize}

% \begin{itemize}
% \item Box building
% \item Droplets
% \item Shrinking
% \end{itemize}

% {\it Cytoplasm Model: }The most abundant non-ribosomal proteins that account for 50\% of the {\em Escherichia coli} xxx cytoplasm's protein composition were chosen for our cytoplasm model~\cite{}. Specifically TufA (pdb 1dg1), MetE (pdb 1u22), IcdA (pdb 1p8f), AhpC(pdb 1yep), CspC (pdb 1mjc), Ppa (pdb 2eip), GapA (pdb 1s7c) and .

% The proteins were simulated at 30\% biomolecular mass fraction in  a physiological salt concentration (0.15M NaCl).

% For all simulations the Amber99sb-ildn force field was used~\cite{Hornak2006, Lindorff2010} in combination with the TIP4P/2005 water model~\cite{Abascal2005b}. Electrostatic interactions were treated using the particle mesh Ewald algorithm~\cite{Essmann1995a} and XXXX. All chemical bonds were constrained at their equilibrium length using the LINCS algorithm~\cite{Hess2008b} allowing an integration time step of 2 fs. Temperature was controlled at 310 K using the v-rescale algorithm~\cite{Bussi2007a} and a coupling time of 0.5 ps. The pressure was controlled at 1 bar using the Parrinello-Rahman algorithm~\cite{Parrinello1981a} with a time constant of 10 ps.

% Among proteins, (the corrections)
% The metabolites structures have been prepared by ... .

% For tRNA and metabolites the vector ... was used.

% \begin{table}
% \centering
% \caption{Proteins PDB ID}
% \label{tbl:pdb}
% \begin{tabular}{lcc}
% \hline
% Protein (pdb)  \\
% \hline
% crowder\_n1 & 1dg1~\cite{Abel1996}   \\ 
% crowder\_n2 & 1u22~\cite{Ferrer2004} \\
% crowder\_n3 & 1p8f~\cite{Mesecar2000} \\
% crowder\_n4 & 1yep~\cite{Parsonage2005}\\
% crowder\_n5 & 1mjc~\cite{Schindelin1994}\\
% crowder\_n6 & 2eip~\cite{Kankare1996}\\
% crowder\_n7 & 1s7c~\cite{ShinXXX}\\
% crowder\_n8 & 1sl4~\cite{Guo2004d}\\
% crowder\_n9 & 1wz2~\cite{FukunagaXXX}\\
% \hline
% \end{tabular}
% \end{table}

% Cytoplasm setup:
% \begin{itemize}
% \item Constitutents of the cytoplasm in ratio, (non-ribomosal) protein, (non-ribosomal) RNA and metabolites {\bf review paper}
% \item Proteins fraction 
% \item Nucleic Acid fraction
% \item Metabolites fraction
% \item Physiological condition of the cell
% \item Biomolecular fraction 
% \end{itemize}

>>>>

@@

@@

@@

\begin{figure}
\includegraphics[scale=0.6]{rdf_mg.pdf}
\caption{Radial distribution function showing the probability of finding a metabolite or an RNA around MG2+.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{avclust.pdf}
\caption{Number of metabolite molecules that form a cluster in cytoplasm simulations. The solid colored lines are the average of three replica (shown in grey).}
\end{figure}

@@

\bibliography{library}
% \begin{addendum}
%  \item  
%  \item[Competing Interests] 
%  \item[Correspondence]  
% \end{addendum}

@@
